---
  title: "Practical ML"
author: "Tanmay Ambegaokar"
date: "21/10/2020"
output: html_document
---
  
  **Synopsis**
  
  Building a prediction model to know how a certain user lifts weights based on data obtained from accelerometer.

The dataset consists on 5 classes:
  
  . The subject is lifting weights exactly according to the specification (Class A).

. Throwing the elbow to the front (Class B).

. Lifting the dumbbell only halfway (Class C).

. Lowering the dumbbell only halfway (Class D).

. Throwing the hips to the front (Class E).


**Getting data**
  
  Training set - "pml-training"
Testing set - "pml-testing"

```{r}
if(!file.exists("pml-training.csv"))
{
  download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", "pml-training.csv", method = 'curl')
}
dataset <- read.csv("pml-training.csv", na.strings = c("NA", ""))
if(!file.exists("pml-testing.csv"))
{
  download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", "pml-testing.csv", method = 'curl')
}
validation <- read.csv("pml-testing.csv")
```

**Data preprocessing**
  
  Import packages.
```{r}
library(caret)
library(randomForest)
```

Set seed for reproducibility.
```{r}
set.seed(17)
```

Partitioning data. 70% - Training, 30% Testing
```{r}
inTrain = createDataPartition(y=dataset$classe, p=0.7, list=FALSE)
train = dataset[inTrain,]
test = dataset[-inTrain,]
```

Eliminate NA
```{r}
NACols = sapply(train, function(x) {sum(is.na(x))}) 
NACols
colsWithNA = names(NACols[NACols > 0]) #Column with NA values
train = train[, !names(train) %in% colsWithNA] 
names(train)
train <- train[, !names(train) %in% c("X", "user_name", "raw_timestamp_part_1", "raw_timestamp_part_2", "cvtd_timestamp", "new_window", "num_window")]
```

Validation set
```{r}
NACols = sapply(validation, function(x) {sum(is.na(x))})
colsWithNA = names(NACols[NACols > 0])
validation = validation[, !names(validation) %in% colsWithNA]
validation <- validation[, !names(validation) %in% c("X", "user_name", "raw_timestamp_part_1", "raw_timestamp_part_2", "cvtd_timestamp", "new_window", "num_window")]
```

Testing set.
```{r}
NACols = sapply(test, function(x) {sum(is.na(x))})
colsWithNA = names(NACols[NACols > 0])
test = test[, !names(test) %in% colsWithNA]
test <- test[, !names(test) %in% c("X", "user_name", "raw_timestamp_part_1", "raw_timestamp_part_2", "cvtd_timestamp", "new_window", "num_window")]
```

Prediction model using Random Forest.

```{r acc}
model <- randomForest(classe ~ .,   data=train, ntree = 50)
predictions <- predict(model, test)
confusionMatrix(predictions, test$classe)
modelAcc <- confusionMatrix(predictions, test$classe)$overall[[1]]
```

Model is `r modelAcc` accurate.

Now, we will predict the unknown classes of the validation set.

```{r}
predictions <- predict(model, validation)
predictions
```